---
title: "Package_architecture"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package_architecture}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(UniversalShrink)
```



# 1. Functions for estimation of the covariance matrix


- Estimator of the covariance matrix using non-linear shrinkage.
  The function is: `analytical_NL_shrinkage()`.
  It is optimal for the Frobenius norm.



# 2. Functions for estimation of the precision matrix




# 3. Functions for estimation of optimal portfolio weights


- From a given precision matrix, one can get the optimal portfolio weights
  (*GMV* for Global Minimum Variance) using the function `GMV_PlugIn()`. This can
  also be used by giving as input an estimator of the precision matrix,
  which then will give as output an estimator of the optimal portfolio weights.

- `GMV_Moore_Penrose()`: using the Moore-Penrose inverse `Moore_Penrose()` of
  the precision matrix as an input for the plug-in estimation.

- `GMV_Moore_Penrose_shrinkage_toEq()`: performs a first-order shrinkage of the
  estimator given by `GMV_Moore_Penrose()` towards the equally-weighted portfolio.




